%%%%%%%%%%%%  Generated using docx2latex.pythonanywhere.com  %%%%%%%%%%%%%%


\documentclass[a4paper,12pt]{report}

% Other options in place of 'report' are 1)article 2)book 3)letter
% Other options in place of 'a4paper' are 1)a5paper 2)b5paper 3)letterpaper 4)legalpaper 5)executivepaper


 %%%%%%%%%%%%  Include Packages  %%%%%%%%%%%%%%


\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{wasysym}
\usepackage{enumitem}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{hhline}
\usepackage{multicol}
\usepackage{float}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{mdwlist}
%\usepackage{fancyhdr}
\usepackage[toc,page]{appendix}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}


 %%%%%%%%%%%%  Define Colors For Hyperlinks  %%%%%%%%%%%%%%


\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=cyan,
}
\urlstyle{same}


 %%%%%%%%%%%%  Set Depths for Sections  %%%%%%%%%%%%%%

% 1) Section
% 1.1) SubSection
% 1.1.1) SubSubSection
% 1.1.1.1) Paragraph
% 1.1.1.1.1) Subparagraph


\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}


 %%%%%%%%%%%%  Set Page Margins  %%%%%%%%%%%%%%


\usepackage[a4paper,bindingoffset=0.0in,headsep=0.5cm,left=0.5in,right=0.5in,bottom=0.5in,top=0.5in,headheight=2cm]{geometry}
\everymath{\displaystyle}


 %%%%%%%%%%%%  Set Depths for Nested Lists created by \begin{enumerate}  %%%%%%%%%%%%%%


\setlistdepth{9}
\newlist{myEnumerate}{enumerate}{9}
	\setlist[myEnumerate,1]{label=\arabic*)}
	\setlist[myEnumerate,2]{label=\alph*)}
	\setlist[myEnumerate,3]{label=(\roman*)}
	\setlist[myEnumerate,4]{label=(\arabic*)}
	\setlist[myEnumerate,5]{label=(\Alph*)}
	\setlist[myEnumerate,6]{label=(\Roman*)}
	\setlist[myEnumerate,7]{label=\arabic*}
	\setlist[myEnumerate,8]{label=\alph*}
	\setlist[myEnumerate,9]{label=\roman*}

\renewlist{itemize}{itemize}{9}
	\setlist[itemize]{label=$\cdot$}
	\setlist[itemize,1]{label=\textbullet}
	\setlist[itemize,2]{label=$\circ$}
	\setlist[itemize,3]{label=$\ast$}
	\setlist[itemize,4]{label=$\dagger$}
	\setlist[itemize,5]{label=$\triangleright$}
	\setlist[itemize,6]{label=$\bigstar$}
	\setlist[itemize,7]{label=$\blacklozenge$}
	\setlist[itemize,8]{label=$\prime$}



 %%%%%%%%%%%%  Header here  %%%%%%%%%%%%%%


%\pagestyle{fancy}
%\fancyhf{}


 %%%%%%%%%%%%  Footer here  %%%%%%%%%%%%%%

\thispagestyle{empty}


 %%%%%%%%%%%%  Print Page Numbers  %%%%%%%%%%%%%%


%\rfoot{\thepage}


 %%%%%%%%%%%%  Document Code starts here %%%%%%%%%%%%%%
\newcommand{\marginAdj}{0.5in}

\begin{document}
\sloppy
{\centering
 \fontsize{12pt}{12pt}\selectfont\textbf{XIANG LI}\\
 \fontsize{11pt}{11pt}\selectfont 424A Pierce St. \\
 \fontsize{11pt}{11pt}\selectfont Bethlehem, PA, 18015 \\
 \fontsize{11pt}{11pt}\selectfont Tel: (669) 271-5090 \\
 \fontsize{11pt}{11pt}\selectfont Email: lixiang.lx618@gmail.com \\
 \fontsize{11pt}{11pt}\selectfont Web: \href{https://github.com/LiXiang618}{\color{black}{\underline{\smash{https://github.com/LiXiang618}}}} \\
}

\vspace{9pt}



\noindent 
\textbf{EDUCATION} \par
\vspace{2pt}
\hrule
\vspace{6pt}
\noindent 
\textbf{Lehigh University, }Bethlehem, PA{\fontsize{9pt}{9pt}\selectfont \textbf{ \hspace*{3.25in} \hspace*{\marginAdj} }{\fontsize{10pt}{10pt}\selectfont Sep, 2016 – present}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{MS, Financial Mathematics, expected May, 2018}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Core Courses: Derivatives, Fixed Income, Econometrics, Optimization, Risk Management, Machine Learning } \par
\end{itemize}
 \par
\noindent 
\textbf{Shanghai Jiao Tong University, }Shanghai, China{\fontsize{9pt}{9pt}\selectfont  \hspace*{2.15in} \hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont Sep, 2012 – Jun, 2016}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{BE, Software Engineering  $  \&  $ Finance}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Core Courses: Programming and Algorithm, Data Structure, Economics, Accounting, Investment, Data Mining} \par
\end{itemize}
 \par
 \vspace{9pt}
 
\noindent 
\textbf{EXPERIENCE} \par
\vspace{2pt}
\hrule
\vspace{6pt}

\noindent 
\textbf{Lehigh University}{\fontsize{9pt}{9pt}\selectfont  \hspace*{4.3in} \hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont Sep, 2017 – present}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{Research Assistant, Finance Department, Bethlehem, PA}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
	\item {\fontsize{10pt}{10pt}\selectfont Conducted event study for big data companies by analyzing the events' impacts on returns and volumes using t-test.} \par
	\noindent 
	\item {\fontsize{10pt}{10pt}\selectfont Assisted in P2P loan study by scraping loan contract data from SEC filings using XML parsing and regular expression in R.} \par
	\noindent 
	\item {\fontsize{10pt}{10pt}\selectfont Studied the features of the Russian option and researched on the optimal exercising time.} \par
\end{itemize}

\noindent 
\textbf{QuantConnect (U.S. Fintech Company)}{\fontsize{9pt}{9pt}\selectfont  \hspace*{2.65in} \hspace*{\marginAdj}  {\fontsize{10pt}{10pt}\selectfont May, 2017 – Aug, 2017}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{Junior Quant Trader Developer}\textit{, }\textit{New York}\textit{, NY}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Facilitated tradings by calculating profit and risk metrics, visualizing results in charts and generating formatted reports in R.} \par
\noindent 
\item {\fontsize{10pt}{10pt}\selectfont Assisted traders' research on derivative products by scraping data from CME website in Python. } \par
\noindent 
\item {\fontsize{10pt}{10pt}\selectfont Conducted research and developed trading strategies based on academic papers for company’s live trading fund.} \par
\item {\fontsize{10pt}{10pt}\selectfont Tested QC research platform's security by attempting to hack data using web scraper and assisted in security improvement.} \par
\noindent 
\end{itemize}

\noindent 
\textbf{Guotai Junan Securities Co., Ltd.}{\fontsize{9pt}{9pt}\selectfont  \hspace*{3.15in}  \hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont Nov, 2015 – Jun, 2016}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{Intern, Quantitative Investment Team, FICC Department Head office, Shanghai, China}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Developed pairs trading strategy based on quantile analysis and co-integration analysis for fixed income products in China.} \par
\item {\fontsize{10pt}{10pt}\selectfont Facilitated tradings by visualizing strategy performances and developing interactive analysis platform using R Shiny.} \par
\end{itemize}

\noindent 
\textbf{Morgan Stanley}{\fontsize{9pt}{9pt}\selectfont  \hspace*{4.4in} \hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont Jul, 2015 – Sep, 2015}} \par
\noindent 
{\fontsize{10pt}{10pt}\selectfont \textit{Summer Intern, Institutional Corporate Technology Department, Shanghai, China}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Guaranteed the correctness of the order control system by building test system and visual platform in python and Java.} \par
\end{itemize}
 \par
\vspace{9pt}



\noindent 
\textbf{PROJECTS} \par
\vspace{2pt}
\hrule
\vspace{6pt}

\noindent
\textbf{The Relation between Stock Momentum and Option Strategies}  \hspace*{\marginAdj}  \hspace*{1.00in} {\fontsize{10pt}{10pt}\selectfont Jan, 2018 – Feb, 2018} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
	\item {\fontsize{10pt}{10pt}\selectfont Replicated the stock momentum strategy by constructing option strategies using Black-Scholes formula.} \par
	\item {\fontsize{10pt}{10pt}\selectfont Enhanced the option portfolio by correcting the payoff asymmetry caused by the relation between stock and VIX returns.} \par
\end{itemize}


\noindent
\textbf{Scenario Analysis on Rebalancing Techniques in Portfolio Management }  \hspace*{\marginAdj}  \hspace*{0.35in} {\fontsize{10pt}{10pt}\selectfont Sep, 2017 – Dec, 2017} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
	\item {\fontsize{10pt}{10pt}\selectfont Evaluated rebalancing strategies by studying simulated market scenarios with varied expected returns and volatilities.} \par
	\item {\fontsize{10pt}{10pt}\selectfont Improved the performance of traditional rebalancing strategy by introducing a signal-triggering mechanism.} \par
\end{itemize}

\noindent 
\textbf{Influence of Fed's Increasing Rates on Global Portfolio}  \hspace*{\marginAdj}  \hspace*{1.55in} {\fontsize{10pt}{10pt}\selectfont Jan, 2017 – Feb, 2017} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Constructed a portfolio taking advantage of rising interest rates by analyzing their effects on global asset markets.} \par
\end{itemize}

\noindent 
\textbf{Optimizing Pairs Trading Strategy by Using Genetic Algorithm} \hspace*{0.95in}  \hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont  Mar, 2016 – Jun, 2016} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Enhanced pairs trading strategy based on co-integration analysis by using Genetic Algorithm optimization.}
\item {\fontsize{10pt}{10pt}\selectfont Displayed the analysis process and results by building interactive visual platform using R Shiny.}
\end{itemize}

\noindent 
\textbf{"Magnet Effect" Under Circuit Breaker System on Chinese Stock Index} \hspace*{0.35in}\hspace*{\marginAdj} {\fontsize{10pt}{10pt}\selectfont Mar, 2016 – Jun, 2016} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
	\item {\fontsize{10pt}{10pt}\selectfont Analyzed the reasons for the failure of the circuit breaker system on Chinese stock index by using GARCH model and conditional probability to describe the "magnet effect" in Chinese stock market in R.} \par
\end{itemize}

 \par
\vspace{9pt}





\noindent 
\textbf{OTHER SKILLS} \par
\vspace{2pt}
\hrule
\vspace{6pt}
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{10pt}{10pt}\selectfont Passed FRM Level I and Level II examinations and CFA Level I examination.} \par
\noindent 
\item {\fontsize{10pt}{10pt}\selectfont Programming skills: R, Python, Matlab, SQL, Stata, Ampl, Java, C++, C, Excel, JavaScript, Html, jQuery, XPath. } \par
\noindent 
\item {\fontsize{10pt}{10pt}\selectfont Additional skills: Regular Expression, Selenium Web Scraper, Git and Github, Linux, Latex, Bloomberg, Thomson Eikon.}\end{itemize}
 \par
\end{document}
